Early environmental conditions do not impact behavioural flexibility in an invasive and non-invasive lizard species

### 2024-09-02 ms.qmd
Updates

Here, we studied the effects of prenatal temperature and corticosterone (CORT) (the main GC in reptiles) [@Crino_2023], on behavioural flexibility in two species of reptiles, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L. guichenoti_). Both species have similar life-histories and overlapping distributions [@chapple_know_2011; @chapple_biology_2014], but only _Lampropholis delicata_ has been successful in colonising different areas around the globe [@baker1979rainbow; @chapple2013divergent; @chapple2015deliinvLHI]. Previous studies exploring behavioral differences between the two species have found _L. delicata_ to be more exploratory than _L. guichenoti_ [@chapple_know_2011], but no differences in learning were observed between the skinks in an associative learning task [@bezzina2014does]. Disparities in behavioural flexibility may be driving the differences in invasion success between both skinks, a prediction supported in other invasive species [@sol2000behavioural; @sol2008brain; @wright2010behavioral; @amiel_smart_2011; @chapple2012can]. However, the relative impact of early environments on behavioural flexibility remains unexplored. Early environments are known to affect suites of morphological and behavioural traits differently in each species [@carrasco2023maternal; @kar2023heritability], but uncertainty still exists about the interactive role of maternal CORT and early temperatures on behavioural flexibility. We manipulated CORT and incubation temperature in both species and then subjected hatchlings to a reversal learning task. Reversal learning, in particular, is a widely employed tool to measure behavioral flexibility [@gapp2014early; @hurtubise2017effects], as it assesses an individual's ability to alter a learned behavior in response to environmental changes, providing researchers with a clear indicator of their ability to adjust to new conditions [@brown2010behavioral].

@@

To empirically test the effect of early environment we manipulated CORT concentration in eggs and incubated them under one of two temperature regimes (Cold -- 23ºC ± 3ºC or Hot -- 30ºC ± 3ºC) in a 2x2 factorial design (@fig-Methods A). We first allocated eggs into one of two different treatments: in the CORT treatment, eggs were topically supplied with 5µL of CORT dissolved in 100% Ethanol (vehicle) at a final concentration of 10 pg CORT/mL; in the Control treatment eggs received an equal volume of the vehicle. CORT concentration employed in the CORT treatment represents 2 standard deviations above the mean natural concentration obtained in eggs from both species (non-published data). Doses were determined by referencing published yolk corticosterone concentrations in other oviparous species [@lovern2008effects ; @hanover2019corticosterone] and our own unpublished data. After the hormone treatment, were then incubated in one of the two previously mentioned temperature regimes (Cold or Hot) until hatching. These temperatures represent the upper and lower limit of the natural incubation temperatures [@qualls2000post; @cheetham2011embryonic]. The number of eggs per clutch assigned to each hormone and temperature treatment were counterbalanced in both species.

@@

#### Statistical analyses  
We performed the analyses for each species separately. We fitted two different Bayesian multilevel models using the brm function from the _brms_ package [@burkner2017brms] using an R extension (version 2.8.2) [@R]. We ran four parallel MCMC chains of 3000 iterations for each model, with a warmup period of 1000 iterations. We modelled correct choices [correct (1) or not (0)] as the response variable, and trial, hormone (CORT versus Control), incubation temperature (Cold versus Hot), and the three-way interaction between trial, hormone, and temperature. The error structure was modeled using a Bernoulli distribution with a logit link function (family = Bernoulli(link = 'logit')). We included a random intercept and slope (trial) for each lizard in our models. We also incorporated the clutch identity as a random factor. _L. delicata_ lays one clutch per year, while _L. guichenoti_ lays two [@chapple_know_2011; @chapple_biology_2014]. Since eggs were collected during half of the breeding season, clutches likely come from different mothers. By including clutch as a random factor, maternal condition should be accounted for in our analyses. Additionally, differential paternity may be captured by including both clutch and lizard identity in the model. Learning can also be age-dependent (see @noble_age-dependent_2014), and given that lizards incubated at different temperatures hatch at different times we explored the effects of age on learning. Indeed, lizards’ age at the beginning of the experiment ranged from 41 to 148 days old in _L. delicata_ and 48 to 132 in _L. guichenoti_. However, when this variable was included in the models we did not find any significant effect of age (see Supplementary material). As such, we present models without age as a fixed effect. We used the posterior distributions of parameters from these models to test for differences in learning rate between treatments and species. Learning slopes were obtained using the ‘trial’ estimates and its interaction with hormone and temperature treatments. Slope estimates greater than zero were considered as evidence of learning, while those less or equal to zero were not. We calculated the probability that slopes or contrasts between slopes differed from zero (p~mcmc~) using the posterior distributions. We considered statistical significance if p~mcmc~ < 0.05.

#### Ethical note
We collected subjects from a breeding colony kept in the lab since 2019. Both the breeding animals and the ones used in this experiment were provided humane laboratory housing, with thermoregulatory opportunities, light (UV and heat) and moderate levels of humidity (see above for details). Lizards in the colony received food ad libitum while the subjects in the experiment were feed one cricket daily during the experiment. All lizards were handled minimally to avoid stress. Experimental procedures and laboratory housing complied with Australian law and were approved by the Australian National University Animal Experimentation Ethics Committee (A2022_33). Animals born in captivity cannot be re-released into the wild as stringent biosafety protocols across the states prohibit this. It is also not possible to rehome such a large number of animals. Therefore, upon completion of experimental trials, lizards were kept in their enclosure until they were humanely euthanized following approved procedures. To euthanise animals, we use an injection of sodium pentobarbital (i.e., Lethabarb) (diluted 1:4 ringers solution) at 60-100mg/kg, injected intrapleuroperitoneally. We monitored the animals to ensure there was no irritation from the agent as indicated by distressed animals. Gently pinching the toes was used to confirm the absence of a response before the animal was disposed of.  
Crickets were maintained in big communal enclosures in the same room where the big colony is, and at the same temperature and light conditions. They were provided vegetables and water ad libitum, and they were given several egg carton shelters to refuge. All lizards were fed alive crickets except during the experiment, when we used crickets frozen at -21 ºC for 24 hours.

@@

Both species learnt across all treatments (@fig-results B, D), but we did not find any difference between treatments or species in the rate of learning (mean slopes per treatment for both species provided in Table 2 in Supplementary Material). For _L. delicata_, hormone treatment (slopes contrast: Control - CORT = `r format_dec(mean(c(deli_ControlCold, deli_ControlHot)) - mean(c(deli_CORTCold, deli_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(deli_ControlCold, deli_ControlHot) - c(deli_CORTCold, deli_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean(c(deli_CORTHot, deli_ControlHot)) - mean(c(deli_CORTCold, deli_ControlCold)),3)`, p~mcmc~ `r format_p(pmcmc(c(deli_CORTHot, deli_ControlHot) - c(deli_CORTCold, deli_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec((mean(deli_ControlHot) - mean(deli_CORTHot)) - (mean(deli_ControlCold) - mean(deli_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc((deli_ControlHot - deli_CORTHot) - (deli_ControlCold - deli_CORTCold)), 3)`) did not affect learning (see @fig-results A, B). We similarly found no significant effects of  hormone (Control - CORT = `r format_dec(mean(c(guich_ControlCold, guich_ControlHot)) - mean(c(guich_CORTCold, guich_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(guich_ControlCold, guich_ControlHot) - c(guich_CORTCold, guich_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean(c(guich_CORTHot, guich_ControlHot)) - mean(c(guich_CORTCold, guich_ControlCold)),3)`, p~mcmc~ `r format_p(pmcmc(c(guich_CORTHot, guich_ControlHot) - c(guich_CORTCold, guich_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec((mean(guich_ControlHot) - mean(guich_CORTHot)) - (mean(guich_ControlCold) - mean(guich_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc((guich_ControlHot - guich_CORTHot) - (guich_ControlCold - guich_CORTCold)), 3)`) on learning in _L. guichenoti_ (see @fig-results C, D).

@@

Finally, when all individuals from all the treatments were pooled together and species were compared, there were not significant differences in the estimated slopes (mean of learning slope in _L. delicata_ = `r format_dec(mean(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot), 0.025), 3)`, `r format_dec(quantile(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot), 0.975), 3)`]; mean learning of slope in _L. guichenoti_ = `r format_dec(mean(c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot), 0.025), 3)`, `r format_dec(quantile(c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot), 0.975), 3)`]; _L. delicata_ - _L. guichenoti_ = `r format_dec(mean(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot)) - mean(c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot) - c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot)), 3)`). Figures for both species with the raw data were included in the Supplementary Material.

@@

#### Results using a standard learning criterion of 5 consecutive correct choices  
Table 3. Number of individuals per treatment and species that reached a learning criterium of 5 consecutive correct choices (n lizards), and the average of trials taken (Trial) together with the standard deviation (sd).  
```{r, tbl-standard_crit, results='asis', out.widht = "26cm"}
#| label: standard_crit
#| tbl-cap: "Number of individuals per treatment and species that reached a learning criterium of 5 consecutive correct choices (n lizards), and the average of trials taken (Trial) together with the standard deviation (sd)."
#
source(here("R", "func.R"))
# Load the data
scrit_df <- clean_df %>%
  group_by(lizard_id,species, trt) %>%
  mutate(
    run_id = cumsum(lag(FC_reversal, default = 0) == 0 & FC_reversal == 1),
    run_length = ave(FC_reversal , run_id, FUN = cumsum) * FC_reversal 
  ) %>%
  filter(run_length >= 5) %>%
  group_by(lizard_id, species, trt) %>%
  slice_min(trial_reversal) %>%  # Get the first trial when the criterion was met
  summarize(
    species = first(species),
    trt = first(trt),
    trial_crit = min(trial_reversal),
    .groups = "drop") %>%
  mutate(trt = factor(trt, 
          levels = c("A_23", "B_23", "A_28", "B_28"), 
          labels = c("Control-Cold", "CORT-Cold", "Control-Hot", "CORT-Hot")),
        species = factor(species,
          levels = c("delicata", "guichenoti"),
          labels = c("L. delicata", "L. guichenoti")))%>%
  group_by(species, trt) %>%
  summarize(
    n = n(),
    mean_trial = format_dec(mean(trial_crit),2),
    des_trial = format_dec(sd(trial_crit),2),
    .groups = "drop") %>%
data.frame()
#
# Create the table
crit_tbl <- flextable(scrit_df) %>%
  set_table_properties(width = 1) %>%
  align(align = "center", part = "all") %>%
  fontsize(size = 10, part = "all") %>%
  set_header_labels(species = "Specie",
                    trt = "Treatment",
                    n = "n lizards",
                    mean_trial = "Mean",
                    des_trial = "sd") %>%
    italic(i = c(1,5), j = 1, italic = TRUE, part = "body") %>% # To have names od species in italics
    flextable::compose(i = c(2:4,6:8), j = 1, value = as_paragraph(""), part = "body") %>% # To remove some of the values in the first column
    hline(i = 4, j = c(1:5), part = "body") %>% # To make some horizontal lines
    autofit()
crit_tbl
```

>>>>

Here, we studied the effects of prenatal temperature and corticosterone (CORT) (the main GC in reptiles) [@Crino_2023], on behavioural flexibility in two species of reptiles, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L. guichenoti_). Both species have similar life-histories and overlapping distributions [@chapple_know_2011; @chapple_biology_2014], but only _Lampropholis delicata_ has been successful in colonising different areas around the globe [@baker1979rainbow; @chapple2013divergent; @chapple2015deliinvLHI]. Previous studies exploring behavioral differences between the two species have found _L. delicata_ to be more exploratory than _L. guichenoti_ [@chapple_know_2011], but no differences in learning were observed between the skinks in an associative learning task [@bezzina2014does]. Disparities in behavioural flexibility may be driving the differences in invasion success between both skinks, a prediction supported in other invasive species [@sol2000behavioural; @sol2008brain; @wright2010behavioral; @amiel_smart_2011; @chapple2012can]. However, the relative impact of early environments on behavioural flexibility remains unexplored. Early environments are known to affect suites of morphological and behavioural traits differently in each species [@carrasco2023maternal; @kar2023heritability], but uncertainty still exists about the interactive role of maternal CORT and early temperatures on behavioural flexibility. We manipulated CORT and incubation temperature in both species and then subjected hatchlings to a reversal learning task. Reversal learning, in particular, is a widely employed tool to measure behavioural flexibility [@gapp2014early; @hurtubise2017effects], as it assesses an individual's ability to reverse a previously learned behaviour providing researchers with a clear indicator of their ability to adjust to new conditions [@brown2010behavioral].

@@

To empirically test the effect of early environment we manipulated CORT concentration in eggs and incubated them under one of two temperature regimes (Cold -- 23ºC ± 3ºC or Hot -- 30ºC ± 3ºC) in a 2x2 factorial design (@fig-Methods A). We first allocated eggs into one of two different treatments: in the CORT treatment, eggs were topically supplied with 5µL of CORT dissolved in 100% Ethanol (vehicle) at a final concentration of 10 pg CORT/mL; in the Control treatment eggs received an equal volume of the vehicle. This method has been validated before in _L. delicata_ [@crino2024eggs], increasing CORT concentration in egg approximately 2 standard deviations above the mean natural concentration. After the hormone treatment, were then incubated in one of the two previously mentioned temperature regimes (Cold or Hot) until hatching. These temperatures represent the upper and lower limit of the natural incubation temperatures [@qualls2000post; @cheetham2011embryonic]. The number of eggs per clutch assigned to each hormone and temperature treatment were counterbalanced in both species.

@@

#### Statistical analyses  
We performed the analyses for each species separately. We fitted two different Bayesian multilevel models using the brm function from the _brms_ package [@burkner2017brms] using an R extension (version 2.8.2) [@R]. We ran four parallel MCMC chains of 3000 iterations for each model, with a warmup period of 1000 iterations. We modelled correct choices [correct (1) or not (0)] as the response variable, and trial, hormone (CORT versus Control), incubation temperature (Cold versus Hot), along with the three-way interaction between trial, hormone, and temperature. If early environments impact learning then we would predict that the rate of learning (i.e., trial slope) varies by treatment as captured by the interactions. The error structure was modelled using a Bernoulli distribution with a logit link function (family = Bernoulli(link = 'logit')). We included a random intercept and slope (trial) for each lizard in our models. We also incorporated the clutch identity as a random factor. _L. delicata_ lays one clutch per year, while _L. guichenoti_ lays two [@chapple_know_2011; @chapple_biology_2014]. Since eggs were collected during half of the breeding season, clutches likely come from different mothers. Additionally, previous research has shown that clutches are generally sired by a single male, but sperm storage can occur [@kar2023heritability]. Given our partial split-clutch design, and the fact that maternal effects are expected to be stronger than paternal effects in these species, including the clutch as a random factor would account for the effects of parental condition. Learning can also be age-dependent [see @noble_age-dependent_2014], and given that lizards incubated at different temperatures hatch at different times we explored the effects of age on learning. Indeed, lizards’ age at the beginning of the experiment ranged from 41 to 148 days old in _L. delicata_ and 48 to 132 in _L. guichenoti_. However, when this variable was included in the models we did not find any significant effect of age (see Supplementary material). As such, we present models without age as a fixed effect. We used the posterior distributions of parameters from these models to test for differences in learning rate between treatments and species. Learning slopes were obtained using the ‘trial’ estimates and its interaction with hormone and temperature treatments. Slope estimates greater than zero were considered as evidence of learning, while those less or equal to zero were not. p~mcmc~ test the hypothesis that slopes and slopes contrasts are zero. We considered statistical significance if pmcmc < 0.05.

#### Ethical note
We collected subjects from a breeding colony kept in the lab since 2019. Both the breeding animals and the ones used in this experiment were provided humane laboratory housing, with thermoregulatory opportunities, light (UV and heat) and moderate levels of humidity (see above for details). Lizards in the colony received food ad libitum while the subjects in the experiment were feed one cricket daily during the experiment. All lizards were handled minimally to avoid stress. Experimental procedures and laboratory housing complied with Australian law and were approved by the Australian National University Animal Experimentation Ethics Committee (A2022_33). Animals born in captivity cannot be re-released into the wild as stringent biosafety protocols across the states prohibit this. It is also not possible to rehome such a large number of animals. Therefore, upon completion of experimental trials, lizards were kept in their enclosure until they were humanely euthanized following approved procedures. To euthanise animals, we use an injection of sodium pentobarbital (i.e., Lethabarb) (diluted 1:4 ringers solution) at 60-100mg/kg, injected intrapleuroperitoneally. We monitored the animals to ensure there was no irritation from the agent as indicated by distressed animals. Gently pinching the toes was used to confirm the absence of a response before the animal was disposed of.  
Crickets were maintained in big communal enclosures (68.5 L x 49 W x 39 H cm) in the same room where the big colony is, and at the same temperature and light conditions. They were provided vegetables and water ad libitum, and they were given several egg carton shelters to refuge. All lizards were fed alive crickets except during the experiment, when we used crickets frozen at -21 ºC for 24 hours.

@@

Both species learnt across all treatments (@fig-results B, D), but we did not find any difference between treatments or species in the rate of learning (mean slopes per treatment for both species provided in Table 2 in Supplementary Material). For _L. delicata_, hormone treatment (β~Control~ - β~CORT~ = `r format_dec(mean(c(deli_ControlCold, deli_ControlHot)) - mean(c(deli_CORTCold, deli_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(deli_ControlCold, deli_ControlHot) - c(deli_CORTCold, deli_CORTHot)), 3)`), incubation temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(deli_CORTHot, deli_ControlHot)) - mean(c(deli_CORTCold, deli_ControlCold)),3)`, p~mcmc~ `r format_p(pmcmc(c(deli_CORTHot, deli_ControlHot) - c(deli_CORTCold, deli_ControlCold)),3)`), or the interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec((mean(deli_ControlHot) - mean(deli_CORTHot)) - (mean(deli_ControlCold) - mean(deli_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc((deli_ControlHot - deli_CORTHot) - (deli_ControlCold - deli_CORTCold)), 3)`) did not affect learning (see @fig-results A, B). We similarly found no significant effects of  hormone (β~Control~ - β~CORT~ = `r format_dec(mean(c(guich_ControlCold, guich_ControlHot)) - mean(c(guich_CORTCold, guich_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(guich_ControlCold, guich_ControlHot) - c(guich_CORTCold, guich_CORTHot)), 3)`), incubation temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(guich_CORTHot, guich_ControlHot)) - mean(c(guich_CORTCold, guich_ControlCold)),3)`, p~mcmc~ `r format_p(pmcmc(c(guich_CORTHot, guich_ControlHot) - c(guich_CORTCold, guich_ControlCold)),3)`), or the interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec((mean(guich_ControlHot) - mean(guich_CORTHot)) - (mean(guich_ControlCold) - mean(guich_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc((guich_ControlHot - guich_CORTHot) - (guich_ControlCold - guich_CORTCold)), 3)`) on learning in _L. guichenoti_ (see @fig-results C, D).

@@

Finally, when all individuals from all the treatments were pooled together and species were compared, there were not significant differences in the estimated slopes (mean of learning slope in _L. delicata_ = `r format_dec(mean(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot), 0.025), 3)`, `r format_dec(quantile(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot), 0.975), 3)`]; mean learning of slope in _L. guichenoti_ = `r format_dec(mean(c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot), 0.025), 3)`, `r format_dec(quantile(c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot), 0.975), 3)`]; β~_L. delicata_~ - β~_L. guichenoti_~ = `r format_dec(mean(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot)) - mean(c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot) - c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot)), 3)`). Figures for both species with the raw data were included in the Supplementary Material.

@@

#### Results using a standard learning criterion of 5 consecutive correct choices  
Table 3. Number of individuals per treatment and species that reached a learning criterion of 5 consecutive correct choices (n lizards), and the average of trials taken (Trial) together with the standard deviation (sd).  
```{r, tbl-standard_crit, results='asis', out.widht = "26cm"}
#| label: standard_crit
#| tbl-cap: "Number of individuals per treatment and species that reached a learning criterion of 5 consecutive correct choices (n lizards), and the average of trials taken (Trial) together with the standard deviation (sd)."
#
source(here("R", "func.R"))
# Load the data
scrit_df <- clean_df %>%
  group_by(lizard_id,species, trt) %>%
  mutate(
    run_id = cumsum(lag(FC_reversal, default = 0) == 0 & FC_reversal == 1),
    run_length = ave(FC_reversal , run_id, FUN = cumsum) * FC_reversal 
  ) %>%
  filter(run_length >= 5) %>%
  group_by(lizard_id, species, trt) %>%
  slice_min(trial_reversal) %>%  # Get the first trial when the criterion was met
  summarize(
    species = first(species),
    trt = first(trt),
    trial_crit = min(trial_reversal),
    .groups = "drop") %>%
  mutate(trt = factor(trt, 
          levels = c("A_23", "B_23", "A_28", "B_28"), 
          labels = c("Control-Cold", "CORT-Cold", "Control-Hot", "CORT-Hot")),
        species = factor(species,
          levels = c("delicata", "guichenoti"),
          labels = c("L. delicata", "L. guichenoti")))%>%
  group_by(species, trt) %>%
  summarize(
    n = n(),
    mean_trial = format_dec(mean(trial_crit),2),
    des_trial = format_dec(sd(trial_crit),2),
    .groups = "drop") %>%
data.frame()
#
# Create the table
crit_tbl <- flextable(scrit_df) %>%
  set_table_properties(width = 1) %>%
  align(align = "center", part = "all") %>%
  fontsize(size = 10, part = "all") %>%
  set_header_labels(species = "Specie",
                    trt = "Treatment",
                    n = "n lizards",
                    mean_trial = "Mean",
                    des_trial = "sd") %>%
    italic(i = c(1,5), j = 1, italic = TRUE, part = "body") %>% # To have names od species in italics
    flextable::compose(i = c(2:4,6:8), j = 1, value = as_paragraph(""), part = "body") %>% # To remove some of the values in the first column
    hline(i = 4, j = c(1:5), part = "body") %>% # To make some horizontal lines
    autofit()
crit_tbl
```
